%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=.85]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Jaydeep} % Your first name
\familyname{Monapara} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{B.Tech. in Computer Engineering (Final Year)}
\address{54, Bhumipark Society,}{Punagam, Surat 395010}
\mobile{(+91) 95749 73454}
\email{jaydeep.monapara54@gmail.com}
\extrainfo{DOB: June 14, 1998}
%\quote{"A witty and playful quotation" - John Smith}
%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2015 - 2019}{Dharamsinh Desai University, Nadiad}{Bachelors of Technology}{}{\textit{Computer Engineering}}{CPI : 8.72 / 10 (Semester 1-6)}

\cventry{2013 - 2015}{Kaushal Vidhyabhavan, Surat}{Higher Secondary Education (HSC)}{}{}{\textit{Percentage : 93.0 \% (Physics, Chemistry, Maths) }}{}

\cventry{2013 - 2015}{Sanskar Vidhyalaya, Surat}{Secondary Education (SSC)}{}{}{\textit{Percentage : 91.5 \%}}{}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
\section{Projects}


\cventry{Feb 2018 - March 2018      }{BillSplit}{}{}{}{This project is aimed at developing an android based mobile application to make it easy to split bills with friends and family. The application organizes all shared expenses at one place, so that everyone can see who they owe. All the data in project is stored in cloud, so user can get access to them anywhere and anytime on their android devices. This project eliminates the need to keep the receipts of every shared expenses.\newline \newline Technologies Used : Java, XML, Firebase Database (Provided By Google) using JSON \newline}

\cventry{Sep 2017 - Oct 2017      }{Online Job Portal}{}{}{}{This project is developed as a part of course-work of subject "Software Engineering". This system make connections of Job Seekers and Job Providers chaos free by providing online platform. In this system, Job Providers can post job vacancies and  and Job Seekers can apply to those jobs. Job Providers can also select job aspirants and send them details for an Interview. The focus of this system is to provide an interface which is user-flexible with reduced man-power.\newline \newline Technologies Used : ASP.NET, AJAX, Bootstrap, MySQL Database \newline}

\cventry{Feb 2017 - March 2017      }{Store Locator}{}{}{}{This system provides an interface to find various stores, hotels and hospitals within range of requested kilometers from a person's location. It shows detailed information of all stores and distance in kilometers from given location on MAP. Store Owners can register their stores with its details on this system.    \newline \newline Technologies Used : PHP, Google MAP API, Materialize CSS, MySQL Database, JavaScript }



%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
\section{Achievements and Co-curricular Activities}


\cvlistitem {Cleared \textbf{NPTEL Online Certification} in \textbf{Fundamental of Database Systems} course with \textbf{Elite Certificate} securing position in \textbf{Top 5\%} Candidates ,within duration of Jul-Sep 2017.}
\cvlistitem {Participated in the \textbf{E-Yantra Robotics Competition (IIT Bombay) - 2017} and reached upto third stage. }
\cvlistitem {Participated in the \textbf{Web Of Things Workshop} organized by \textbf{Mozilla India} at FootPrints 2016, MS University, Vadodara. }
\cvlistitem {Participated in the seminar of \textbf{Networking and Security} organized by \textbf{CSI-DDU Student Branch} on January 3, 2017. }
%----------------------------------------------------------------------------------------
%	Skills SECTION
%----------------------------------------------------------------------------------------

\section{Skills}

\cvitem{Proficient in }{C, Java, Algorithms, MySQL, ASP.NET}
\cvitem{Basic Ability With }{C\#, Android, PHP, Matlab, Assembly, Firebase, JSON, XML, Bootstrap}
\cvitem{IDE }{NetBeans, VisualStudio, Android Studio}

%----------------------------------------------------------------------------------------
%	Coursework SECTION
%----------------------------------------------------------------------------------------

\section{Courses}

\cvlistitem{Data Structures and Algorithms}
\cvlistitem{Database Management Systems}
\cvlistitem{Software Engineering}
\cvlistitem{Operating Systems}
\cvlistitem{Web Development}
\cvlistitem{Service Oriented Architecture}

%----------------------------------------------------------------------------------------
%	Personal Information SECTION
%----------------------------------------------------------------------------------------

\section{Personal Information}

\cvlistitem{\textbf{Father's Name :} Vallabhbhai D. Monapara (Diamond Worker)}
\cvlistitem{\textbf{Mother's Name :} Shivkurben V. Monapara (House-Wife)}
\cvlistitem{\textbf{Languages Known :} English, Hindi, Gujarati}

%----------------------------------------------------------------------------------------
%	Declaration SECTION
%----------------------------------------------------------------------------------------

\section{Declaration}

{
\cvitem{}{I hereby declare that the above mentioned information is correct up to my knowledge and I bear the responsibility for correctness of the above mentioned particular. }
}


%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}



