%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Document Configs
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{jaydeep-resume-openfont}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

%\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Jaydeep}{Monapara}
{ \href{mailto:jaydeep.mmonapara54@gmail.com}{jaydeep.monapara54@gmail.com} | (+91) 9574973454 }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.29\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Dharmsinh Desai \newline University, Nadiad}
\descript{BTech in Computer Engineering }
\location{ 2015 |  2019 }
\location{ CPI : 8.78 / 10.0}
\sectionsep

\subsection{Kaushal Vidyabhavan, \newline Surat}
\location{Higher Secondary School | 2015}
\location{Merit - 93.0 \% }
\sectionsep

\subsection{Sanskar Vidhyalaya, \newline Surat}
\location{Secondary School | 2013}
\location{Merit - 91.50\%}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}

Github:// \href{https://github.com/jaydeep3969}{\bf jaydeep3969} \\
LinkedIn://  \href{https://in.linkedin.com/in/jaydeep-monapara-a70a48119}{\bf jaydeep-monapara} \\
Codechef:// \href {https://www.codechef.com/users/jaydeep_3969}{\bf jaydeep\textunderscore 3969} \\
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Coursework}

%\textbullet{} Data Structures \\
%\textbullet{} Algorithms \\
%\textbullet{} Database Systems \\
%\textbullet{} Operating Systems \\
%\textbullet{} Basics of Service Oriented Architecture \\
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\textbullet{} Data Structures and Algorithms \\
\textbullet{} Object Oriented Programming \\
\textbullet{} REST Web-Services \\
\textbullet{} C/C++ \textbullet{} Python \\
\textbullet{}  NodeJS with Express (Basics)\\
\textbullet{} Angular8 \textbullet{} Ionic \\
\textbullet{} PrimeNG \textbullet{} Materialize \\
\textbullet{} MySQL \textbullet{} MongoDB \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Achievements and Co-Curricular Activities
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements}

\textbullet{} Cleared \textbf{NPTEL Online Certification} in \textbf{Fundamental of Database Systems} course with \textbf{Elite Certificate} securing position in \textbf{Top 5\%} Candidates ,within duration of Jul-Sep 2017.\\
\textbullet{} Successfully completed \textbf{E-Yantra Robotics Competition (2017)} hosted by IIT Bombay.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Details
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Personal Details}
\textbullet{} \textbf{Date of Birth:} 14/06/1998 \\
\textbullet{} \textbf{Languages known:} English, Hindi\\ and Gujarati.\\
\textbullet{} \textbf{Permanent address:} 54, Bhumipark Society;\\  Punagam; Surat,\\ Gujarat, India-395010.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.70\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Infosys Ltd}
\descript{| System Engineer}
\location{August 2019 – Present | Bangalore, India}
\textbullet{} Working as a front-end developer to develop a web-app using \textbf{Angular8} and a hybrid mobile-app using \textbf{Ionic} Framework which are the Vehicle Inventory Management platforms for Mercedes-Benz.\\
\textbullet{} Working with team on design and development of offline mode and geotagging vehicles features, in ionic-mobile app. \\
\textbullet{} Experience with developing multi theme support for both the apps as well as performance analysis and optimizations. \\
\sectionsep

\runsubsection{Infosys Ltd}
\descript{| System Engineer Intern}
\location{Dec 2018 – April 2019 | Mysore-Pune, India}
\textbullet{} Got trained for \textbf{Python}  development and developed basic applications.\\
\textbullet{} Worked as front-end developer to build an Employee and Project Management web-app with use of \textbf{Angular7} for Cummins Corporation. \\
\textbullet{} Redesigned database for the same platform in \textbf{MongoDB}. \\
\textbullet{} Implemented a module to import data from excelsheet to MongoDB using Python. \\
\textbullet{} Developed multiple Proof-of-Concepts in \textbf{MEAN stack} in order to implement Authentication using JWT, Server Creation using Express, REST Web Services and APIs. \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}

\runsubsection{Dev Management}
\descript{| May 2019}
\location{\href{https://github.com/jaydeep3969/DEV-MEAN}{\bf //github.com/jaydeep3969/dev-management}}
\location{Technologies Used : MEAN Stack (MongoDB, Express, Angular, NodeJS) }
\textbf{Description:} This is a summer vacation project developed for an enterprise managing three different types of businesses in Surat. It is a web-app for Inventory Management, Customers and their EMIs Management, Invoice Generation and Financial Monitoring for all businesses at common platform.\\
\sectionsep

\runsubsection{Roster Tracker \bf (Internship)}
\descript{| Mar 2018 - Apr 2019}
\location{Technologies Used : Angular7, Java Spring Boot, MongoDB}
\textbf{Description:} This project is part of the internship at Infosys. It is a web-app which provides facilities to manage Employees and their Billings, Projects and Roster Report Generation.\\
\sectionsep

\runsubsection{BillSplit}
\descript{| Feb 2018 - March 2018}
\location{\href{https://github.com/jaydeep3969/billsplit}{\bf //github.com/jaydeep3969/billsplit}}
\location{Technologies used: Android (Java, XML), Firebase DB (By Google) using JSON }
\textbf{Description:} This is an android app to make easy to split bills with friends and family. The app organizes all shared expenses at one place, so that everyone can see who they owe.\\
\sectionsep

\runsubsection{Online Job Portal}
\descript{| Sep 2017 - Oct 2017}
\location{\href{https://github.com/jaydeep3969/Online-Job-Portal}{\bf //github.com/jaydeep3969/online-job-portal}}
\location{Technologies used: ASP.NET, AJAX, Bootstrap, MySQL DB}
\textbf{Description:} This project is developed as part of course-work of subject "Software Engineering". This system make connections of Job Seekers and Job Providers chaos free by providing online platform. In this system, Job Providers can post job vacancies and  and Job Seekers can apply to those jobs. It also recommends jobs based on prefernces.
\sectionsep

\runsubsection{Store Locator}
\descript{| Feb 2017 - March 2017}
\location{\href{https://github.com/jaydeep3969/Store-Locator}{\bf //github.com/jaydeep3969/store-locator}}
\location{Technologies used: PHP, Google MAP API, Materialize CSS, MySQL DB, JavaScript}
\textbf{Description:} This is an interface to find various stores, hotels, hospitals etc. within range of requested kilometers from a person's location on Map. It shows detailed information of all stores and distance in kilometers. Store Owners can register their stores on this system.
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}
